Airline Customer Satisfaction - Group 17

### 2025-03-26 Draft Business Analytics Assignment Group 17.Rmd
Add EDA

```{r}
data$Flight.Distance[data$Flight.Distance %in% boxplot(data$Flight.Distance)$out] = median(data$Flight.Distance)
data$Arrival.Delay[data$Arrival.Delay %in% boxplot(data$Arrival.Delay)$out] = median(data$Arrival.Delay)
data$Departure.Delay[data$Departure.Delay %in% boxplot(data$Departure.Delay)$out] = median(data$Departure.Delay)
```

>>>>

```{r}
data$Flight.Distance[which(
  data$Flight.Distance > (quantile(data$Flight.Distance, 0.75, na.rm = TRUE) + 1.5 * IQR(data$Flight.Distance, na.rm = TRUE))
)] <- median(data$Flight.Distance, na.rm = TRUE)

data$Arrival.Delay[which(
  data$Arrival.Delay > (quantile(data$Arrival.Delay, 0.75, na.rm = TRUE) + 1.5 * IQR(data$Arrival.Delay, na.rm = TRUE))
)] <- median(data$Arrival.Delay, na.rm = TRUE)

data$Departure.Delay[which(
  data$Departure.Delay > (quantile(data$Departure.Delay, 0.75, na.rm = TRUE) + 1.5 * IQR(data$Departure.Delay, na.rm = TRUE))
)] <- median(data$Departure.Delay, na.rm = TRUE)
```

Now we can see the distribution of the data after the imputation.

```{r}
plot_histogram(data[ , c('Flight.Distance','Arrival.Delay','Departure.Delay')], ncol=2,ggtheme = theme_minimal())
```

```{r}
ggplot(data, aes(x=Departure.Delay)) +
geom_boxplot(fill = 2,alpha = 0.5,color = 1,outlier.colour = 2) +
theme_bw()
```
```{r}
ggplot(data, aes(x=Arrival.Delay)) +
geom_boxplot(fill = 2,alpha = 0.5,color = 1,outlier.colour = 2) +
theme_bw()
```

### Association Between Two Numerical Variable

```{r}
library(corrplot)
```

```{r}
numeric_data <- data[sapply(data, is.numeric)]
numeric_data <- na.omit(numeric_data)

# Compute correlation matrix
cor_matrix <- cor(numeric_data)

# Print the correlation matrix
print(cor_matrix)

# Visualize the correlation matrix
options(repr.plot.width=10, repr.plot.height=8)
corrplot(cor_matrix,
         method = "color",       # Use colored squares
         type = "upper",         # Show only upper triangle
         order = "hclust",       # Cluster similar variables together
         tl.col = "black",       # Text color
         tl.srt = 45,            # Label text rotation
         tl.cex = 0.8,           # Label text size
         number.cex = 0.7,       # Correlation number size
         addCoef.col = "black",  # Show correlation numbers
         diag = FALSE)           # Hide diagonal (all 1s)
```

```{r}
# Discover strong correlation
cor_matrix_flat <- as.data.frame(as.table(cor_matrix))
filtered <- subset(cor_matrix_flat, abs(Freq) > 0.5 & Var1 != Var2)
filtered <- filtered[!duplicated(t(apply(filtered[, 1:2], 1, sort))), ]

print(filtered)
```

In-flight comfort and service such as Seat Comfort, Leg Room Service, Cleanliness, Food and Drink, In-flight Service, In-flight Wifi Service, and In-flight Entertainment are highly correlated with each other. This is expected as they are all related to the comfort and service provided during the flight.

Digital service such as Ease of Online Booking, Online Boarding, and In-flight Wifi Service are also highly correlated with each other. This is expected as they are all related to the digital service provided by the airline.

```{r}
count_data <- as.data.frame(table(data$In.flight.Service, data$On.board.Service))
count_data$Percent <- round(100 * count_data$Freq / sum(count_data$Freq), 1)

# Plot heatmap
ggplot(count_data, aes(x = Var1, y = Var2, fill = Percent)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Percent, "%")), color = "black", size = 3) +
  scale_fill_gradient(low = "lightyellow", high = "darkred") +
  labs(title = "In-flight Service vs On-board Service (in %)",
       x = "In-flight Service Rating",
       y = "On-board Service Rating",
       fill = "Percentage") +
  theme_minimal()
```

```{r}
count_data <- as.data.frame(table(data$In.flight.Entertainment, data$Food.and.Drink))
count_data$Percent <- round(100 * count_data$Freq / sum(count_data$Freq), 1)

# Plot heatmap
ggplot(count_data, aes(x = Var1, y = Var2, fill = Percent)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Percent, "%")), color = "black", size = 3) +
  scale_fill_gradient(low = "lightyellow", high = "darkred") +
  labs(title = "In-flight Entertainment vs Food and Drink (in %)",
       x = "In-flight Entertainment Rating",
       y = "Food and Drink Rating",
       fill = "Percentage") +
  theme_minimal()
```

```{r}
count_data <- as.data.frame(table(data$In.flight.Entertainment, data$Cleanliness))
count_data$Percent <- round(100 * count_data$Freq / sum(count_data$Freq), 1)

# Plot heatmap
ggplot(count_data, aes(x = Var1, y = Var2, fill = Percent)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Percent, "%")), color = "black", size = 3) +
  scale_fill_gradient(low = "lightyellow", high = "darkred") +
  labs(title = "In-flight Entertainment vs Cleanliness (in %)",
       x = "In-flight Entertainment Rating",
       y = "Cleanliness Rating",
       fill = "Percentage") +
  theme_minimal()
```

```{r}
count_data <- as.data.frame(table(data$In.flight.Entertainment, data$Seat.Comfort))
count_data$Percent <- round(100 * count_data$Freq / sum(count_data$Freq), 1)

# Plot heatmap
ggplot(count_data, aes(x = Var1, y = Var2, fill = Percent)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Percent, "%")), color = "black", size = 3) +
  scale_fill_gradient(low = "lightyellow", high = "darkred") +
  labs(title = "In-flight Entertainment vs Seat Comfort (in %)",
       x = "In-flight Entertainment Rating",
       y = "Seat Comfort Rating",
       fill = "Percentage") +
  theme_minimal()
```

```{r}
count_data <- as.data.frame(table(data$Food.and.Drink, data$Cleanliness))
count_data$Percent <- round(100 * count_data$Freq / sum(count_data$Freq), 1)

# Plot heatmap
ggplot(count_data, aes(x = Var1, y = Var2, fill = Percent)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Percent, "%")), color = "black", size = 3) +
  scale_fill_gradient(low = "lightyellow", high = "darkred") +
  labs(title = "Food and Drink vs Cleanliness (in %)",
       x = "Food and Drink Rating",
       y = "Cleanliness Rating",
       fill = "Percentage") +
  theme_minimal()
```

```{r}
count_data <- as.data.frame(table(data$Food.and.Drink, data$Seat.Comfort))
count_data$Percent <- round(100 * count_data$Freq / sum(count_data$Freq), 1)

# Plot heatmap
ggplot(count_data, aes(x = Var1, y = Var2, fill = Percent)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Percent, "%")), color = "black", size = 3) +
  scale_fill_gradient(low = "lightyellow", high = "darkred") +
  labs(title = "Food and Drink vs Seat Comfort (in %)",
       x = "Food and Drink Rating",
       y = "Seat Comfort Rating",
       fill = "Percentage") +
  theme_minimal()
```

```{r}
count_data <- as.data.frame(table(data$Cleanliness, data$Seat.Comfort))
count_data$Percent <- round(100 * count_data$Freq / sum(count_data$Freq), 1)

# Plot heatmap
ggplot(count_data, aes(x = Var1, y = Var2, fill = Percent)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Percent, "%")), color = "black", size = 3) +
  scale_fill_gradient(low = "lightyellow", high = "darkred") +
  labs(title = "Cleanliness vs Seat Comfort (in %)",
       x = "Cleanliness Rating",
       y = "Seat Comfort Rating",
       fill = "Percentage") +
  theme_minimal()
```

```{r}
count_data <- as.data.frame(table(data$In.flight.Wifi.Service, data$Ease.of.Online.Booking))
count_data$Percent <- round(100 * count_data$Freq / sum(count_data$Freq), 1)

# Plot heatmap
ggplot(count_data, aes(x = Var1, y = Var2, fill = Percent)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Percent, "%")), color = "black", size = 3) +
  scale_fill_gradient(low = "lightyellow", high = "darkred") +
  labs(title = "In-Flight Wifi Service vs Ease of Online Booking (in %)",
       x = "In-Flight Wifi Service Rating",
       y = "Ease of Online Booking Rating",
       fill = "Percentage") +
  theme_minimal()
```

```{r}
ggplot(data, aes(x = Flight.Distance, y = Departure.Delay)) +
  geom_point(alpha = 0.2, color = "steelblue", size = 1.5) +
  labs(title = "Flight Distance vs Departure Delay",
       x = "Flight Distance",
       y = "Departure Delay") +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 1) +
  theme_minimal()
```

```{r}
ggplot(data, aes(x = Flight.Distance, y = Arrival.Delay)) +
  geom_point(alpha = 0.2, color = "steelblue", size = 1.5) +
  labs(title = "Flight Distance vs Arrival Delay",
       x = "Flight Distance",
       y = "Arrival Delay") +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 1) +
  theme_minimal()
```
